---
title: "lab_2"
author: "Yan Ting Lala Wong"
date: "07/02/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab 2
# Name: Yan Ting Wong
# SFU ID: 301386593

#1 
Simulate some test data as follows:
```{r}
set.seed(1)
x1 <- 1:100
x2 <- rnorm(100); x3 <- rnorm(100)
y <- x1+rnorm(100)
data <- data.frame(y,x1,x2,x3)
```

#2 
Write a couple of lines of R code to (i) fit a model with `lm()`
with response variable y and predictors x1, x2 and x3 and (ii) use
`step()` on the fitted model to do stepwise model reductions.
In your call to lm, use the `.` in your formula and pass it the 
data frame constructed in the code chunk.
```{r}
fit <- lm(y~., data = data)
summary(fit)

step(fit)

# y only depends on x1, so it is significant
```


#3
Now try to do the same thing using your `mars()` function from lab
1 with the following modifications. 
Recall that your `mars()` function
took an R formula, `data` and `control` as inputs 
and called functions `fwd_stepwise()` and `bwd_stepwise()`.
    a. Pass the formula and data arguments to `fwd_stepwise()`. 
    Have `fwd_stepwise()` call the `lm()` function on the
    formula and data and return the resulting `lm` object.
    b. As in lab 1, your `bwd_stepwise()` function takes the output
    of `fwd_stepwise()`. Now have `bwd_stepwise()` call the 
    `step()` function on its input, and return the output of `step()`.
    c. As in lab 1, your `mars()` function returns the output of `bwd_stepwise()`. 
    d. Test your implementation with the call `mars(y~.,data=data)`.
```{r}
mars <- function(formula, data, contol=list()) {
  
  fwd_out <- fwd_stepwise(formula, data) # Add formula and data arguments

  bwd_out <- bwd_stepwise(fwd_out, data)

  return(bwd_out) 
}

mars.control <- function() {
  
  control <- list()
  
  return(control)
}

fwd_stepwise <- function(formula, data) # Add formula and data arguments
{
  
  fwd_lst <- lm(formula, data) # replace list() with lm()
  
  return(fwd_lst)
  
}

bwd_stepwise <- function(bwd_in, data) {
  
  bwd_lst <- step(bwd_in) # relace with step()
  
  return(bwd_lst)
  
}

mars(y~., data = data)
```

4. Change the name of the data frame `data` in your workspace
to `testdata` are re-run mars. What happens? Use `traceback()`
to identify the function call that threw an error. What does this
tell you about where this function found the data in part 3?
```{r}
testdata <- data
rm(data)
mars(y~., data = testdata)
```

